---
title: "10-import"
output:
  html_document:
    df_print: paged
---

```{r libraries}
library(readr)
library(assertr)
library(tidyverse)
library(janitor)
library(magrittr)
```


## Introduction

This dataset is originally from the National Institute of Diabetes and Digestive and Kidney Diseases. The objective of the dataset is to diagnostically predict whether or not a patient has diabetes, based on certain diagnostic measurements included in the dataset. Several constraints were placed on the selection of these instances from a larger database. In particular, all patients here are females at least 21 years old of Pima Indian heritage.

This dataset is licencsed under CC0:Public Domain.


## Import Dataset

This is a "CSV" format dataset.

```{r}
diabetes <- read_csv("diabetes.csv")
```

## Checking the Values

First the names and the dimensions

```{r names&dim}
names(diabetes)
dim(diabetes)
```

The names of the columns are pretty clean.Some names are multiple words.

```{r clean_name}
diabetes <- clean_names(diabetes)
names(diabetes)
```

The words are seperated by dash after cleaning. 



Now lets check if there is NA.

```{r check_NA}
sum(is.na(diabetes))>0


```


There is no NA in the data.


## Check the values(Assert)


According to the dataset the minimum age of the woman is 21. Let's see if it is true in the dataset.

```{r assert_age}
diabetes %>%
  assert(within_bounds(21,100),age)
```

Assert returns no error. So the age of the women are above 21 and below 100.

### Other Columns


### Blood Pressure

Averge Blood Pressure for woman of 21 year of age is above 80mm Hg. 30mm Hg means very low blood pressure.

```{r pressure_check}
diabetes %>% 
  assert(within_bounds(30,Inf),blood_pressure)
```
There are 5 rows with 0 in blood pressure column. But blood pressure cannot be zero. So these must be NAs.

### Glucose
The glucose level are plasma glucose concentration.

They can get as low as 30.

```{r glucose_check}
diabetes %>% 
  assert(within_bounds(30,Inf), glucose)
```

Glucose Columns have NA too which are the 0 values.

Skin thickness and BMI has wide range. Let's check if there are any 0 in it.

```{r bmi_skinT_check}
sum(diabetes$skin_thickness == 0) > 0
sum(diabetes$bmi == 0) > 0
```

So skin thickness and and BMI both have 0 values.


The same test will not be conducted for Insulin column. Because if a person does not have diabetes that person does not need insulin.So the insulin having value 0 is valid.



The outcome column can only have 0 or 1. It signifies if a person have diabetes or not.

```{r outcome_check}
diabetes %>% assert(in_set(c(0,1)),outcome)
```

So the values are 0 or 1 which is correct.

# Recoding the missing values

The missing values in this dataset are 0 except for the insulin and pregnancies column.


```{r missing_value}
df <- diabetes %>% select(everything(),-pregnancies,-outcome,-insulin) %>% na_if(0)
diabetes <- df %>% mutate(pregnancies=diabetes$pregnancies,outcome= diabetes$outcome,insulin=diabetes$insulin)
diabetes <- diabetes %>% select(outcome,everything())
diabetes

```
In this project we are going to use machine learning to predict chances of a pima Indian woman having diabetes.
