---
title: "30-feature-engineering"
output: html_notebook
---
## Feature Engineering

Sometimes discrete variables work better than continuous models for some machine learning models like random forest and clustering. 

Keeping this in mind, two variables Insulin level and  will be categorised according to medical practice.


## Catagorize Insulin Level.

This function will take in the whole data frame and check the the insulin level. If the insulin level is below 166 then it will return 0 otherwise 1 in a new column called "insulin_cat"

0 is normal insulin level and 1 is abnormal insulin level.

Note: "Outcome" is our target variable. so "outcome" and "insulin_cat" are selected to be at the front of columns. 

```{r cat_insulin}


cat_insulin <- function(df)
{df%>% 
  mutate_at(c("insulin"),list(insulin_cat=function(x)ifelse(x<166,0,1)))  %>%
    select(c(outcome,insulin_cat),everything())
}



```





```{r test_insulin_cat}
test <-  diabetes %>% cat_insulin() %>% select(insulin,insulin_cat)
test %>% filter(insulin>=166) %>% nrow

sum(test$insulin_cat)



```
The number of times insulin_cat gives 1 is equal to number of times insulin level is greater than 166.

So the function is working.



## Catagorize BMI
Now we categorise BMI.

BMI can be underweight, healthy, overweight and obese accrodin to their respective BMI.


The function will take in the whole data frame and give a new column called bmi_cat using the last. The output will be like below.

BMI      | Category   |Function Output
0-18.5   | Underweight| 0
18.5-24.9| Healthy    | 1
24.9-30  | Overweight | 2
30-over  | Obese      | 3




```{r bmi_cat}

bmi_cat <- function(df){
df%>% 
  mutate(bmi,bmi_cat=cut(bmi,breaks=c(0, 18.5, 24.9, 30,Inf), 
                   labels=c(0,1,2,3))) %>% 
    select(c(outcome,bmi_cat),everything())
  }

```



```{r test_bmi_cat}
x <- c(0,1,2,3)
diabetes %>% bmi_cat %>% assert(in_set(x),bmi_cat)

```

The assert shows all the values are well within range.
The function is working.


## Stadardize Age
Lets's standardize the age. Not having NA would not change anthing as there is no NA in 

```{r standardize}
scale2 <- function(x,na.rm=FALSE )(x-mean(x,na.rm=na.rm))/sd(x,na.rm=na.rm)
std_age <- function(df)
{df%>% 
  mutate_at(c("age"),list(age_std=scale)) 
}

diabetes %>% std_age()


```

## Detecting Early Marriage

If a woman has 2 or more pregnancy before 23. We can classify it as early marriage.


```{r early_not}

early2 <- function(x)ifelse(x$age<23&x$pregnancies>2,"Early","Not Early")
diabetes$early <- diabetes %>% early2


early_marriage <- function(df){
  
  df%>% 
  mutate_at(c("age","pregnancies"),list(insulin_cat=function(x,y)ifelse(x<23&y>2,"Early","Not Early"))) 
  
}

df %>% early_marriage()
```

