---
title: "30-feature-engineering"
output:
  html_document:
    df_print: paged
---
```{r}
library(magrittr)
```

## Feature Engineering

Sometimes discrete variables work better than continuous models for some machine learning models like random forest and clustering. 

Keeping this in mind, two variables Insulin level and  will be categorized according to medical practice.


## Categorize Insulin Level.

This function will take in the whole data frame and check the the insulin level. If the insulin level is below 166 then it will return 0 otherwise 1 in a new column called "insulin_cat"

0 is normal insulin level and 1 is abnormal insulin level.

Note: "Outcome" is our target variable. so "outcome" and "insulin_cat" are selected to be at the front of columns. 

```{r cat_insulin}


cat_insulin <- function(df)
{df%>% 
  mutate_at(c("insulin"),list(insulin_cat=function(x)ifelse(x<166,0,1)))  %>%
    select(c(outcome,insulin_cat),everything())
}



```



Now we test the function

```{r test_insulin_cat}
test <-  diabetes %>% cat_insulin() %>% select(insulin,insulin_cat)
test %>% filter(insulin>=166) %>% nrow

sum(test$insulin_cat)

test %>% assert(in_set(c(0,1)),insulin_cat)

```
The number of times insulin_cat gives 1 is equal to number of times insulin level is greater than 166.

So the function is working.Also assert says it is in set of 0,1.



## Categorize BMI
Now we categories BMI.

BMI can be underweight, healthy, overweight and obese according to their respective BMI.


The function will take in the whole data frame and give a new column called bmi_cat using the last. The output will be like below.

BMI      | Category   |Function Output
0-18.5   | Underweight| 0
18.5-24.9| Healthy    | 1
24.9-30  | Overweight | 2
30-over  | Obese      | 3




```{r bmi_cat}

cat_bmi <- function(df){
df%>% 
  mutate(bmi,bmi_cat=cut(bmi,breaks=c(0, 18.5, 24.9, 30,Inf), 
                   labels=c(0,1,2,3))) %>% 
    select(c(outcome,bmi_cat),everything())
  }

```
Note there will be some NA in the bmi_cat column as there was bmi.


```{r test_bmi_cat}
x <- c(0,1,2,3)
diabetes %>% cat_bmi %>% assert(in_set(x),bmi_cat)

```

The assert shows all the values are well within range.
The function is working.

